Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-05-04 hotstorage13/eval.tex
correction
fix some numbers

The seek cost of each random IO request in our test machines is about  10 milliseconds.
The average I/O usage of local storage is controlled about 50MB/second for backup. 
in the presence of other I/O jobs. Noted that a typical 1U server can host
6 to 8  hard drives and deliver over 300MB/second. Our setting uses 16.7\% or less 
of local storage bandwidth. 
The final snapshots are stored in a distributed file system built on the same 
cluster.

@@

Figure~\ref{fig:memory} shows the total parallel time in hours to backup 2500 VMs on
 a 100-node cluster a  when 
limit $M$ imposed on each node varies.
%  from 20MB to 200MB.
This figure also depicts the time breakdown for Stages 1, 2, and 3. 
%The parallel time includes the first scanning time, 
%of dirty VM segments to generate block fingerprints, data redistribution for request accumulation,
%fingerprint comparison, duplicate summary distribution, and the second scan time for real backup.
The time in Stages 1 and 3  is  dominated by  the two scans of dirty segments,
and final data copying to the backup storage is overlapped with VM scanning.
During dirty segment reading, the average number of consecutive dirty segments is 2.92. 
%Each scan takes about 1.4 hours.
The overall processing time does not have a significant reduction as $M$ increases to 200MB.
The aggregated deduplication throughput is  about 9.6GB per second,
which is the size of 2500 VM images divided by the parallel time. 
The system runs with  a single thread and  its CPU resource usage is 10-13\% of one core. 
The result shows the backup with multi-stage deduplication  for all VM images can be 
completed in about 2.9 hours with 35MB memory,  8GB disk overhead and a small CPU usage.
As we vary the cluster size $p$,  the parallel time does  not change much, and  the aggregated throughput
scales up linearly since the number of VMs is  $25p$.

Table~\ref{tab:overall} shows performance change when limit $M$=35MB is imposed and
the number of partitions per machine ($q$) varies.
% varies from 100 to 1000.
Row 2 is memory space required to load a partition of global index and detection requests.
When $q=100$, the required memory is 100.1 MB and this exceeds the limit $M=$35MB.  
Row 3 is the parallel time and Row 4 is  the aggregated throughput of  100 nodes.
%The result shows the backup with multi-phase deduplication  for all VM images can be completed in about 3.09 hours
%with the very small resource usage.
Row 5 is  the parallel time for using Option 1 with $p\times q$ send buffers 
described in Section~\ref{sect:arch}. 
When $q$ increases, the available space per buffer reduces and there is a big increase of seek cost.  
The main network usage before performing the final data write is for request accumulation and
summary output. It lasts about 20 minutes and each machine exchanges 
about   8MB of metadata per second with others during that period, which is 6.25\% of the network bandwidth.

\begin{table}[hbt]
\caption{ Performance when $M$=35MB and $q$ varies.}
\begin{center}
\begin{tabular} {|c|c|c|c|c|c|}
\hline \#Partitions ($q$)  & 100 & 250  & 500 &  750 &  1000 \\
\hline Index+request & 100.1 &  40.1 & 20.1 & 13.4 & 10.1 \\
  (MB)           &  &   &  & &  \\

\hline Total Time  & N/A&  2.9 & 2.91 & 3 & 3.1 \\
  (Hours)           &  &   &  & &  \\
%\hline Throughput/node & N/A&  85MB/s& 90M & 87 & 81 \\
\hline Throughput GB/s& N/A&  9.6& 9.5 & 9.3 & 8.9 \\
\hline Total time & N/A&  7.8& 11.7 & 14.8 & 26 \\
  (Option 1)           &  &   &  & &  \\
\hline
\end{tabular}
\end{center}
\label{tab:overall}
\end{table}

>>>>

The seek cost of each random IO request in our test machines is about  10 milliseconds.
The average I/O usage of local storage is controlled about 50MB/second for backup 
in the presence of other I/O jobs. Noted that a typical 1U server can host
6 to 8  hard drives and deliver over 300MB/second. Our setting uses 16.7\% or less 
of local storage bandwidth. 
The final snapshots are stored in a distributed file system built on the same 
cluster.

@@

Figure~\ref{fig:memory} shows the total parallel time in hours to backup 2500 VMs on
 a 100-node cluster a  when 
limit $M$ imposed on each node varies.
%  from 20MB to 200MB.
This figure also depicts the time breakdown for Stages 1, 2, and 3. 
%The parallel time includes the first scanning time, 
%of dirty VM segments to generate block fingerprints, data redistribution for request accumulation,
%fingerprint comparison, duplicate summary distribution, and the second scan time for real backup.
The time in Stages 1 and 3  is  dominated by  the two scans of dirty segments,
and final data copying to the backup storage is overlapped with VM scanning.
During dirty segment reading, the average number of consecutive dirty segments is 2.92. 
%Each scan takes about 1.4 hours.
The overall processing time does not have a significant reduction as $M$ increases to 95MB.
The aggregated deduplication throughput is  about 8.76GB per second,
which is the size of 2500 VM images divided by the parallel time. 
The system runs with  a single thread and  its CPU resource usage is 10-13\% of one core. 
The result shows the backup with multi-stage deduplication  for all VM images can be 
completed in about 3.1 hours with 35MB memory,  8GB disk overhead and a small CPU usage.
As we vary the cluster size $p$,  the parallel time does  not change much, and  the aggregated throughput
scales up linearly since the number of VMs is  $25p$.

Table~\ref{tab:overall} shows performance change when limit $M$=35MB is imposed and
the number of partitions per machine ($q$) varies.
% varies from 100 to 1000.
Row 2 is memory space required to load a partition of global index and detection requests.
When $q=100$, the required memory is 83.6 MB and this exceeds the limit $M=$35MB.  
Row 3 is the parallel time and Row 4 is  the aggregated throughput of  100 nodes.
%The result shows the backup with multi-phase deduplication  for all VM images can be completed in about 3.09 hours
%with the very small resource usage.
Row 5 is  the parallel time for using Option 1 with $p\times q$ send buffers 
described in Section~\ref{sect:arch}. 
When $q$ increases, the available space per buffer reduces and there is a big increase of seek cost.  
The main network usage before performing the final data write is for request accumulation and
summary output. It lasts about 20 minutes and each machine exchanges 
about   8MB of metadata per second with others during that period, which is 6.25\% of the network bandwidth.

\begin{table}[hbt]
\caption{ Performance when $M$=35MB and $q$ varies.}
\begin{center}
\begin{tabular} {|c|c|c|c|c|c|}
\hline \#Partitions ($q$)  & 100 & 250  & 500 &  750 &  1000 \\
\hline Index+request & 83.6 &  33.5 & 16.8 & 11.2 & 8.45 \\
  (MB)           &  &   &  & &  \\

\hline Total Time  & N/A&  3.12 & 3.15 & 3.22 & 3.29 \\
  (Hours)           &  &   &  & &  \\
%\hline Throughput/node & N/A&  85MB/s& 90M & 87 & 81 \\
\hline Throughput GB/s& N/A&  8.76 & 8.67 & 8.48 & 8.30 \\
\hline Total time & N/A&  7.8& 11.7 & 14.8 & 26 \\
  (Option 1)           &  &   &  & &  \\
\hline
\end{tabular}
\end{center}
\label{tab:overall}
\end{table}
